Using Sorghum as an outgroup to find syntenic regions in Maize: regenerating

### 2017-09-01 SubGenome Analysis.Rmd
Minor

# source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\parseSubgenomes.R")
# source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\addGOTerms.R")
```

>>>>

# source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\loadData.R")
# source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\cleanData.R")
# source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\parseSubgenomes.R")
# source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\addGOTerms.R")
# source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\parseGOSlim.R")
# # source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\createTopGO.R")
# source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\parseExpressionData.R")
```
